\LARGE \bf Experimental Validation of Reference Spreading by Robotic Manipulation of Unmodeled Objects

### 2023-01-07 QP.tex
Wayyy better notation

\text{\textbf{Reference Spreading}}\\
\varphi  \quad \text{Time of impact}\\
\gamma  \quad \text{Normalized time since impact}\\
T  \quad \text{Duration of interim impact mode}\\
m \quad \text{Intermediate impact mode selector (0: no RS, 1: Jari, 2: Sven, 3: mixing)}\\
j \quad \text{Number of jumps that have occured}\\\\
\text{\textbf{Sub- and superscripts}}\\
(\cdot)_{dem} \quad \text{Signals from VR device during recording}\\
(\cdot)_{rec} \;\quad \text{Signals measured from robot or calculated during recording}\\
(\cdot)_{ext} \;\quad \text{Signals resulting from the splitting and extending of the recorded signal}\\
(\cdot)_{ref} \;\quad \text{Signals determined using RS scheme}\\
(\cdot)_{rep} \;\quad \text{Signals measured from robot or calculated during replay}\\
\end{array}$
\newpage
\section*{Recording}

@@

\includegraphics[trim={1cm 17.8cm 5cm 6.5cm}, clip]{Graphics/qp.pdf}
\\
\section*{Reference Extending}
$\begin{array}{l}
S_{hold}(x,\varphi,t,j) 
= \begin{cases} 
x(\varphi_j),& \text{if } t< \varphi_j\\
x(\varphi_j),& \text{if } t> \varphi_{j+1} \\
x(t) ,& \text{otherwise}\\
\end{cases}\\
\\

S_{integ}(x,y,\varphi,t,j) 
= \begin{cases} 
x(\varphi_j)+y(\varphi_j)(t-\varphi_j),& \text{if } t< \varphi_j\\
x(\varphi_{j+1})+y(\varphi_{j+1})(t-\varphi_{j+1}),& \text{if } t> \varphi_{j+1}  \\
x(t) ,& \text{otherwise}\\
\end{cases}\\
\\

S_{rot}(R,\omega,\varphi,t,j) 
= \begin{cases} 
R(\varphi_j)e^{\omega(\varphi_j)(t-\varphi_j)},& \text{if } t< \varphi_j\\
R(\varphi_{j+1})e^{\omega(\varphi_{j+1})(t-\varphi_{j+1})},& \text{if } t> \varphi_{j+1}\\
R(t) ,& \text{otherwise}\\
\end{cases}\\
\\

@@

R_{ext,j}(t) = S_{rot}(R_{rec},\omega_{rec},\varphi_{rec},t,j)\\

\\
\begin{bmatrix} 
p_{ext,j}(t)  \\
 q_{1,ext,j}(t) 
\end{bmatrix} = S_{integ} \left (
\begin{bmatrix} 
p_{rec}\\
 q_{1,rec}
\end{bmatrix} 
,\begin{bmatrix} 
v_{rec}\\
 \dot{q}_{1,rec}
\end{bmatrix} 
,\varphi_{rec},t,j \right )\\
\\

\\
\begin{bmatrix} 
\omega_{rec}(t)\\
v_{ext,j}(t)\\
 \dot{q}_{1,ext,j}(t)\\
 f_{ext,j}(t)\\
 \beta_{ext,j}(t)
\end{bmatrix} = S_{hold} \left (
\begin{bmatrix} 
\omega_{rec}\\
v_{rec}\\
 \dot{q}_{1,rec}\\
 f_{rec}\\
 \beta_{rec}
\end{bmatrix}
,\varphi_{rec},t,j \right )\\
\\

@@

\section*{Reference Switching}

@@

U_{jump}(x,x_{ext},\gamma,m,j) = \begin{cases} 
x_{ext,j},& \text{if } \gamma \geq 1\\

x_{ext,j},& \text{if } (\gamma < 1)\wedge(m=0)\\ 
x,& \text{if } (\gamma < 1)\wedge(m=1)\\ 
0,& \text{if } (\gamma < 1)\wedge(m=2)\\ 
\gamma x_{ext,j} ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\
\\
U_{cont}(x_{ext},\gamma,m,j) = \begin{cases} 
x_{ext,j},& \text{if } \gamma \geq 1\\

x_{ext,j},& \text{if } (\gamma < 1)\wedge(m=0)\\ 
x_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=1)\\ 
x_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=2)\\ 
\gamma x_{ext,j}+ (1-\gamma)x_{ext,j-1} ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\\\

U_{rot}(R_{ext},\gamma,m,j) = \begin{cases} 
R_{ext,j},& \text{if } \gamma \geq 1\\

R_{ext,j},& \text{if } (\gamma < 1)\wedge(m=0)\\ 
R_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=1)\\ 
R_{ext,j-1},& \text{if } (\gamma < 1)\wedge(m=2)\\ 
R_{ext,j-1}(R^T_{ext,j-1}R_{ext,j})^\gamma,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\

R_{ref} = U_{rot}(R_{ext},\gamma,m,j)\\

\\
\begin{bmatrix} 
p_{ref}  \\
 q_{1,ref} \\
 \dot{q}_{1,ref}\\
 f_{ref}\\
 \beta_{ref}
\end{bmatrix} = U_{cont} \left (
\begin{bmatrix} 
p_{ext}\\
 q_{1,ext}\\
 \dot{q}_{1,ext}\\
 f_{ext}\\
 \beta_{ext}
\end{bmatrix} 
,\gamma, m , j \right )\\
\\

\\
\begin{bmatrix} 
\omega_{ref}\\
v_{ref}\\
\end{bmatrix} = U_{jump} \left (
\begin{bmatrix} 
\omega_{ext,j}(t)\\
v_{ext,j}(t)\\
\end{bmatrix}
,\varphi_{rec},\gamma,m,j \right )\\
\\

\newpage

>>>>

\text{\textbf{Reference Spreading}}\\
\varphi  \quad \text{Time of impact}\\
\Delta \varphi \; \text{Offset between measured impact and reference extension}\\
\gamma  \quad \text{Normalized time since impact}\\
T  \quad \text{Duration of interim impact mode}\\
m \quad \text{RS mode selector (-1: no RS, 
0: no interim, 1: Jari, 2: Sven, 3: mixing)}\\
j \quad \text{Number of jumps that have occured}\\\\
\text{\textbf{Sub- and superscripts}}\\
(\cdot)_{dem} \quad \text{Signals from VR device during recording}\\
(\cdot)_{rec} \;\quad \text{Signals measured from robot or calculated during recording}\\
(\cdot)_{ext} \;\quad \text{Signals resulting from the splitting and extending of the recorded signal}\\
(\cdot)_{ref} \;\quad \text{Signals determined using RS scheme}\\
(\cdot)_{rep} \;\quad \text{Signals measured from robot or calculated during replay}\\
\end{array}$
\newpage
\section*{Recording}

@@

\includegraphics[trim={1cm 17.8cm 5cm 6.5cm}, clip]{Graphics/qp.pdf}
\\
\section*{Reference Extending}
$\begin{array}{l}

$$\varphi_{rec}^- = \varphi_{rec}(j)+\Delta \varphi$$\\
$$\varphi_{rec}^+ = \varphi_{rec}(j+1)-\Delta \varphi$$\\
\\
$$\Omega = \begin{bmatrix}
0 & -\omega_3 & \omega_2\\ 
\omega_3 & 0 &-\omega_1 \\ 
 -\omega_2 & \omega_1 & 0
\end{bmatrix}$$\\
\\
S_{hold}(x) 
= \begin{cases} 
x(\varphi_{rec}^-),& \text{if } t< \varphi_{rec}^-\\
x(\varphi_{rec}^+),& \text{if } t> \varphi_{rec}^+\\
x(t) ,& \text{otherwise}\\
\end{cases}\\
\\

S_{integ}(x,y) 
= S_{hold}(x)+\begin{cases} 
y(\varphi_{rec}^-)(t-\varphi_{rec}^+),& \text{if } t< \varphi_{rec}^-\\
y(\varphi_{rec}^+)(t-\varphi_{rec,j}^-),& \text{if } t> \varphi_{rec}^+\\
0 ,& \text{otherwise}\\
\end{cases}\\
\\

S_{rot}(R,\omega) 
= \begin{cases} 
R(\varphi_{rec}^-)e^{\Omega(\varphi_{rec}^-)(t-\varphi_{rec}^-)},& \text{if } t< \varphi_{rec}^-\\
R(\varphi_{rec}^+)e^{\Omega(\varphi_{rec}^+)(t-\varphi_{rec}^+)},& \text{if } t> \varphi_{rec}^+\\
R(t) ,& \text{otherwise}\\
\end{cases}\\
\\

@@

R_{ext,j}(t,j) = S_{rot}(R_{rec}(t),\omega_{rec}(t))\\

\\
\begin{bmatrix} 
p_{ext,j}(t,j)  \\
 q_{1,ext,j}(t,j) 
\end{bmatrix} = S_{integ} \left (
\begin{bmatrix} 
p_{rec}(t)\\
 q_{1,rec}(t)
\end{bmatrix} 
,\begin{bmatrix} 
v_{rec}(t)\\
 \dot{q}_{1,rec}(t)
\end{bmatrix} 
 \right )\\
\\

\\
\begin{bmatrix} 
\omega_{rec}(t,j)\\
v_{ext}(t,j)\\
 \dot{q}_{1,ext}(t,j)\\
 f_{ext}(t,j)\\
 \beta_{ext}(t,j)
\end{bmatrix} = S_{hold} \left (
\begin{bmatrix} 
\omega_{rec}(t)\\
v_{rec}(t)\\
 \dot{q}_{1,rec}(t)\\
 f_{rec}(t)\\
 \beta_{rec}(t)
\end{bmatrix}
\right )\\
\\

@@

Note that the functions $S_{hold}$, $S_{integ}$, and $S_{rot}$ als require $\varphi_{rec}$ to be evaluated. This dependancy is excluded from notation for brevity. 
\section*{Reference Switching}

@@

U_{jump}(x_{rep},x_{ext}) = \begin{cases} 
x_{ext}(t,j_{rec}),& \text{if } m = -1\\
x_{ext}(t,j_{rep}),& \text{if } m = 0\\
x_{ext}(t,j_{rep}),& \text{if } (\gamma \geq 1)\wedge (m \notin \{ -1,0 \} )\\
x_{ext}(t,j_{rep}),& \text{if } (\gamma < 1)\wedge(m=0)\\ 
x,& \text{if } (\gamma < 1)\wedge(m=1)\\ 
0,& \text{if } (\gamma < 1)\wedge(m=2)\\ 
\gamma x_{ext}(t,j_{rep}) ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\
\\

U_{cont}(x_{ext}) = \begin{cases} 
x_{ext}(t,j_{rec}),& \text{if } m = -1\\
x_{ext}(t,j_{rep}),& \text{if } m = 0\\
x_{ext}(t,j_{rep}),& \text{if } (\gamma \geq 1)\wedge (m \notin \{ -1,0 \} )\\
x_{ext}(t,j_{rep}) ,& \text{if } (\gamma < 1)\wedge(m=0)\\ 
x_{ext}(t,j_{rep}-1) ,& \text{if } (\gamma < 1)\wedge(m=1)\\ 
x_{ext}(t,j_{rep}-1) ,& \text{if } (\gamma < 1)\wedge(m=2)\\ 
\gamma x_{ext}(t,j_{rep})+ (1-\gamma)x_{ext}(t,j_{rep}-1) ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\\\
\\

U_{cont}(R_{ext}) = \begin{cases} 
R_{ext}(t,j_{rec}),& \text{if } m = -1\\
R_{ext}(t,j_{rep}),& \text{if } m = 0\\
R_{ext}(t,j_{rep}),& \text{if } (\gamma \geq 1)\wedge (m \notin \{ -1,0 \} )\\
R_{ext}(t,j_{rep}) ,& \text{if } (\gamma < 1)\wedge(m=0)\\ 
R_{ext}(t,j_{rep}-1) ,& \text{if } (\gamma < 1)\wedge(m=1)\\ 
R_{ext}(t,j_{rep}-1) ,& \text{if } (\gamma < 1)\wedge(m=2)\\ 
R_{ext}(t,j_{rep}-1)(R^T_{ext}(t,j_{rep}-1)R_{ext}(t,j_{rep}))^\gamma ,& \text{if } (\gamma < 1)\wedge(m=3)\\ \end{cases}\\\\\\

R_{ref}(t) = U_{rot}(R_{ext}(t,j))\\

\\
\begin{bmatrix} 
p_{ref}(t) \\
 q_{1,ref}(t) \\
 \dot{q}_{1,ref}(t)\\
 f_{ref}(t)\\
 \beta_{ref}(t)
\end{bmatrix} = U_{cont} \left (
\begin{bmatrix} 
p_{ext}(t,j)\\
 q_{1,ext}(t,j)\\
 \dot{q}_{1,ext}(t,j)\\
 f_{ext}(t,j)\\
 \beta_{ext}(t,j)
\end{bmatrix} 
 \right )\\
\\

\\
\begin{bmatrix} 
\omega_{ref}(t)\\
v_{ref}(t)\\
\end{bmatrix} = U_{jump} \left (

\begin{bmatrix} 
\omega_{rep}(t)\\
v_{rep}(t)\\
\end{bmatrix},

\begin{bmatrix} 
\omega_{ext}(t,j)\\
v_{ext}(t,j)\\
\end{bmatrix}

\right )\\
\\
\end{array}$
Note that the functions $U_{jump}$, $U_{cont}$, and $U_{rot}$ als require $j_{rep}$, $j_{rec}$, $\gamma$ and $m$ to be evaluated. These dependencies are excluded from notation for brevity. 
\newpage
